Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
radius -> radii

\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
Moltres and the \gls{ORNL} \gls{MSRE} design model. The radius for the
plots are chosen to correspond to the peak of the thermal flux in both cases;
for the \gls{ORNL} calculations this is 8.4 inches from the core center-line
because of the effect of the control rod thimbles and extra fuel along the
center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
calculations include the lower and upper plena which are not included in this
report's Moltres model. Consequently, the plot in \cref{fig:msre_axial_fluxes}
extends to lower and higher z-values than
\cref{fig:moltres_axial_fluxes}. Additionally, absorption in the plena caused 
deviation of the thermal flux from a sinusoidal shape in 
\cref{fig:msre_axial_fluxes}.

>>>>

\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
Moltres and the \gls{ORNL} \gls{MSRE} design model. The radii for the
plots are chosen to correspond to the peak of the thermal flux in both cases;
for the \gls{ORNL} calculations this is 8.4 inches from the core center-line
because of the effect of the control rod thimbles and extra fuel along the
center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
calculations include the lower and upper plena which are not included in this
report's Moltres model. Consequently, the plot in \cref{fig:msre_axial_fluxes}
extends to lower and higher z-values than
\cref{fig:moltres_axial_fluxes}. Additionally, absorption in the plena caused 
deviation of the thermal flux from a sinusoidal shape in 
\cref{fig:msre_axial_fluxes}.
